### 2018-01-30 README.Rmd
minor admin updates
add funding notices

---
output:
  rmarkdown::github_document
bibliography: README-refs.bib
---

@@

The development of this software was supported in part through a grant from the
National Library of Medicine of the NIH (T32 LM012417).

>>>>

---
output:
  rmarkdown::github_document
bibliography: "`r here::here('README-refs.bib')`"
---

@@

The development of this software was supported in part through grants from the
National Institutes of Health: [T32 LM012417](https://projectreporter.nih.gov/project_info_description.cfm?aid=9248418&icde=37849831&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC&pball=), [R01 ES021369](https://projectreporter.nih.gov/project_info_description.cfm?aid=9210551&icde=37849782&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC&pball=), and [P42 ES004705-29](https://projectreporter.nih.gov/project_info_details.cfm?aid=9260357&map=y).
